---
output: github_document
---

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/robinlovelace/transportAPI?branch=master&svg=true)](https://ci.appveyor.com/project/robinlovelace/transportAPI)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# transportAPI

The goal of transportAPI is to provide a simple R interface to the transportAPI.net routing service.

It was split-out from **stplanr** for modularity.

## Installation

<!-- You can install the released version of transportAPI from [CRAN](https://CRAN.R-project.org) with: -->
Install the package with **devtools** as follows:

```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("mem48/transportAPI")
```

## Example

A common need is to get from A to B:

```{r example}
library ("transportAPI")
# stplanr::geo_code ("leeds rail station") 
from = c(-1.544, 53.794)
# stplanr::geo_code ("leeds university") 
to = c(-1.551, 53.807)
r = transportAPI::journey(from, to)
sf:::plot.sf(r)
```

To get a key go to https://developer.transportapi.com/

Save the key as an environment varible using `export TRANSPORTAPI_app_id=your_id_here` by adding `TRANSPORTAPI_app_id=your_id_here` as a new line in your `.Renviron` file and `TRANSPORTAPI_app_key=your_key_here`, e.g. with the following command:

```{r, eval=FALSE}
usethis::edit_r_environ()
```

Route types available are: public, car, cycle
See help pages such as `?journey` and https://developer.transportapi.com/ for details.

