---	---
output: github_document	output: github_document
---	---
<!-- README.md is generated from README.Rmd. Please edit that file -->
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,	 
  comment = "#>",	
  fig.path = "man/figures/README-",	
  out.width = "100%"
)
```
# transportAPI	# Open Trip Planner for R


 The goal of transportAPI is to provide a simple R interface to the transportAPI.com service.	The goal of Open Trip Planner for R is to provide a simple R interface to the Open Trip Planner.


 It was split-out from **stplanr** for modularity.	#

 ## Installation	
 ## Installation - R Package


Install the package with **devtools** as follows:	Install the package with **devtools** as follows:


```{r, eval=FALSE}
devtools::install_github("ITSleeds/transportAPI")	
```

## Example
A common need is to get from A to B:	

```{r, eval=FALSE}	
library(transportAPI)	
library(sf)	
library(dplyr)	
from = c(-0.432, 51.52)	
to = c(0.012, 51.52)	
r.public = transportAPI::journey(from, to, base_url = "http://fcc.transportapi.com/")	
sf:::plot.sf(r.public[r.public$route_option == 1,"mode"], lwd = 3)	
r.car = transportAPI::journey(from, to, base_url = "http://fcc.transportapi.com/", apitype = "car")	
sf:::plot.sf(r.car[,"mode"], lwd = 3)	
```	

 To get a key go to https://developer.transportapi.com/	

 Save the key as an environment varible using `export TRANSPORTAPI_app_id=your_id_here` by adding `TRANSPORTAPI_app_id=your_id_here` as a new line in your `.Renviron` file and `TRANSPORTAPI_app_key=your_key_here`, e.g. with the following command:	

```{r, eval=FALSE}	
usethis::edit_r_environ()	
```	

 Route types available are: public, car, cycle	
See help pages such as `?journey` and https://developer.transportapi.com/ for details.	
