---
title: "Intorduction to TransportAPI"
author: "Malcolm Morgan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The goal of 'transportAPI' is to provide a simple R interface to the TransportAPI (<https://www.TransportAPI.com/>) routing/data API. This API provides multimodal A-B routing, and as well as other data such as stations, timetables, and more.

## Installation

Install the package with remotes as follows:

```{r, eval = FALSE}
# install.packages("remotes") # Only if you do not have the remotes package already
remotes::install_github("ITSleeds/transportAPI")
library(transportAPI)
```

This package is not yet aviaible on CRAN as it still in Beta stage.

## Getting setup with Transport API

To use transportAPI you need an account. You can signup at https://developer.transportapi.com/ for a free API key.

You need to have an api key and app id for this code to run.
By default it uses the TRANSPORTAPI_app_id and  TRANSPORTAPI_app_key environment variable.
This can be set with `usethis::edit_r_environ()`.

## Getting routes

The function `tapi_journey()` returns a route from A to B.

```{r, eval =TRUE}
from = c(-0.134649,51.529258) # Euston Station
to = c(-0.088780,51.506383) # Bridge House
r1 = transportAPI::tapi_journey(from, to)
plot(r1["mode"])
```


